Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-06-21 main.tex
fix merge conflicts plus more changes in response to reviewers

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that they cannot be gamed, meaning that forecasters (anyone or anything that issues a forecast) are incentivised to report their true belief about the future. In expectation, a forecaster receives the best score if their forecast $F$ coincides with the data-generating distribution $G$, that is if $F = G$. Common proper scoring rules are the logarithmic or log score \citep{goodRationalDecisions1952} or the continuous ranked probability score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007}. The log score is the log-likelihood of the predictive density at the observed value and is scale-invariant under monotonous transformations. The log score does not suffer from the issues we address in this paper, but due to a number of reasons is not as widely used in fields such as weather forecasting or epidemiology (see e.g., \citealt{Johansson2019} for an exception). For example, the log score assigns particularly severe penalties to occasional misguided forecasts. This lack of robustness may limit its practical applicability \citep{bracherEvaluatingEpidemicForecasts2021}. Moreover, it is not easily applied to forecasts reported as samples or quantiles, as used in many recent disease forecasting efforts. 
For these reasons, the CRPS or its discrete equivalent, the ranked probability score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the weighted interval score ~\citep[WIS,][]{bracherEvaluatingEpidemicForecasts2021} are more commonly used in epidemiology.

@@

For conceptual clarity and to allow for a more in-depth discussion, we focus mostly on the natural logarithm as a particular transformation in the context of epidemic phenomena. We refer to this transformation as 'log-transformation' and to scores that have been log-transformed as scores 'on the log scale' (as opposed to scores 'on the natural scale', which have not been transformed). In the theoretical discussion in Section \ref{sec:methods}, 'log-transformation' and 'log scale' generally refer to a transformation of $\log_{e}(x)$. For practical applications (Section \ref{sec:HUB}) we also use these terms to describe a transformation of $\log_{e}(x + \varepsilon)$ in order to keep the notation simple. For a prediction target with strictly positive support, the CRPS after applying a log-transformation is given by
%
\begin{linenomath*}
\begin{equation}
    \text{CRPS}(F_{\log}, \log y) = \int_{-\infty}^\infty \left( F_{\log}(x) - \boldsymbol{1}(x \geq \log y) \right)^2 dx.
\end{equation}    
\end{linenomath*}
%
Here, $y$ is again the observed outcome and $F_{\log}$ is the predictive CDF of the log-transformed outcome, i.e.,
\begin{linenomath*}
\begin{equation}
F_{\log}(x) = F(\exp(x)),
\end{equation}    
\end{linenomath*}
with $F$ the CDF on the original scale. Instead of a score representing the magnitude of absolute errors, applying a log-transformation prior to the CRPS yields a score which a) measures relative error (see Section \ref{sec:methods:relative}), b) provides a measure for how well a forecast captures the exponential growth rate of the target quantity (see Section \ref{sec:methods:growthrate}) and c) is less dependent on the expected order of magnitude of the quantity to be predicted (see Section \ref{sec:methods:vst}). 
We therefore argue that such evaluations on the logarithmic scale should complement the prevailing evaluations on the natural scale. 
Other transformations may likewise be of interest. We briefly explore the square root transformation as an alternative transformation. 
Our analysis mostly focuses on the CRPS (or WIS) as an evaluation metric for probabilistic forecasts, given its widespread use throughout the COVID-19 pandemic.

@@

To illustrate the effect of applying the natural logarithm prior to evaluating forecasts we consider the absolute error, which the CRPS and WIS generalize to probabilistic forecasts. We assume strictly positive support (meaning that no specific handling of zero values is needed), a restriction we will address when applying this transformation in practice. When considering a point forecast $\hat{y}$ for a quantity of interest $y$, such that 
%
\begin{linenomath*}
\begin{equation}
y = \hat{y} + \varepsilon,
\end{equation}
\end{linenomath*}
the absolute error is given by $|\varepsilon|$. When taking the logarithm of the forecast and the observation first, thus considering 
\begin{linenomath*}
\begin{equation}
\log y = \log \hat{y} + \varepsilon^*,
\end{equation}
\end{linenomath*}
the resulting absolute error $\left|\varepsilon^*\right|$ can be interpreted as an approximation of various common relative error measures. Using that $\log(a) \approx a - 1$ if $a$ is close to 1, we get
\begin{linenomath*}
\begin{equation}
|\varepsilon^*| = |\log \hat{y} - \log y| = \left|\log\left(\frac{\hat{y}}{y}\right) \right| \ \ \stackrel{\text{if } \hat{y} \ \approx \ y}{\approx} \ \ \left| \frac{\hat{y}}{y} - 1 \right| \ \ = \ \ \left| \frac{\hat{y} - y}{y} \right|.
\end{equation}
\end{linenomath*}
The absolute error after log transforming is thus an approximation of the \textit{absolute percentage error} \citep[APE,][]{gneitingMakingEvaluatingPoint2011a} as long as forecast and observation are close. As we assumed that $\hat{y} \approx y$, we can also interpret it as an approximation of the \textit{relative error} (RE, \citealt{gneitingMakingEvaluatingPoint2011a})
\begin{linenomath*}
\begin{equation}
\left| \frac{\hat{y} - y}{\hat{y}} \right|
\end{equation}
\end{linenomath*}
and the \textit{symmetric absolute percentage error} (SAPE; see e.g., \citealt{Flores1986})
\begin{linenomath*}
\begin{equation}
\left| \ \frac{\hat{y} - y}{y/2 + \hat{y}/2} \ \right|.
\end{equation}
\end{linenomath*}
As Figure \ref{fig:SAPE} shows, the alignment with the SAPE is in fact the closest and holds quite well even if predicted and observed value differ by a factor of two or three. Generalising to probabilistic forecasts, the CRPS applied to log-transformed forecasts and outcomes can thus be seen as a probabilistic counterpart to the symmetric absolute percentage error, which offers an appealing intuitive interpretation.

@@

When evaluating models across sets of forecasting tasks, it may be desirable for each target to have a similar impact on the overall results. This is true if one assumes that forecasts for different targets provide similar amounts of information about how well a forecaster performs. Ideally, one would like the magnitude of the score to scale with the difficulty of the prediction tasks and the information that can be obtained about overall performance of the forecaster. In disease incidence forecasting, however, CRPS values on the natural scale typically scale with the order of magnitude of the quantity to be predicted. Average scores are then dominated by the results achieved for targets with high expected outcomes in a way that does not necessarily reflect the underlying predictive ability well.

@@

If the mean-variance relationship is quadratic with $\sigma^2 = c \times \mu^2$, the natural logarithm can serve as the VST \citep{guerreroTimeseriesAnalysisSupported1993}. Denoting by $F_{\log}$ the predictive distribution for $\log(Y)$, we can use the delta method (a first-order Taylor approximation, see e.g., \citealt{Dunn2018}), to show that
\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.\label{eq:taylor_quadratic}
\end{equation}
\end{linenomath*}
The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections \ref{sec:methods:relative} and \ref{sec:methods:growthrate}. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome.

@@

Transformations that are strictly monotonic are permissible in the sense that resulting scores remain proper. This is because even though rankings of models may change forecasts will in expectation still minimise their score if they report a predictive distribution that is equal to the data-generating distribution. This condition holds for both the log and square root transformations, as well as many others. However, the order of the operations matters, and applying a transformation after scores have been computed generally does not guarantee that the score remains proper. In the case of log transforms, taking the logarithm of the scores, rather than scoring the log-transformed forecasts and data, results in an improper score. This is because taking the logarithm of the CRPS (or WIS) results in a score that does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

In practice, one issue with the log transform is that they are not readily applicable to negative numbers or zero values, which need to be removed or otherwise handled. 
One common approach to deal with zeros is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm \citep{bellegoDealingLogsZeros2022}. This represents a strictly monotonic transformation and therefore guarantees that the resulting score remains proper. The choice of the quantity to add does however influence scores and rankings, as measures of relative errors shrink when adding a constant $a$ to the forecast and the observation. We illustrate this in Figure \ref{fig:illustration-effect-log-offset}. As a rule of thumb, if if $x > 5a$, the difference between $\log{(x + a)}$ and $\log{(x)}$ is small, and it becomes negligible if $x > 50a$. Choosing a suitable offset $a$ balances two competing concerns: on the one hand, choosing a small $a$ makes sure that the transformation is as close to a natural logarithm as possible and scores can be interpreted as outlined above. On the other hand, choosing a larger $a$ can help stabilise scores for forecasts and observations close to zero, avoiding giving excessive weight to forecasts for small quantities (see Figure \ref{fig:HUB-log-different-offsets}).

A related issue occurs when the predictive distribution has a large probability mass on zero (or on very small values), as this can translate into an excessively wide forecast in relative terms. This can be seen in Figure \ref{fig:HUB-model-comparison-baseline}. Here, the dispersion component of the WIS is inflated for scores obtained after applying the natural logarithm because forecasts contained zero in its prediction intervals.

@@

\subsection{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on the CRPS may change when making use of a transformation, both in terms of aggregate and individual scores. We illustrate this in Figure \ref{fig:illustration-ranking} with two forecasters, A and B, issuing two different distributions with different dispersion. When showing the obtained CRPS as a function of the observed value, it can be seen that the ranking between the two forecasters may change when scoring the forecast on the logarithmic, rather than the natural scale. In particular, on the natural scale, forecaster A, who issues a more uncertain distribution, receives a better score than forecaster B for observed values far away from the centre of the respective predictive distribution. On the log scale, however, forecaster A receives a lower score for large observed values, being more heavily penalised for assigning large probability to small values (which, in relative terms, are far away from the actual observation). We note that the chosen example involving a geometric forecast distribution is somewhat constructed; for more similarly shaped pairs of forecast distributions this phenomenon will not typically occur.

@@

The forecasts used for the purpose of this illustration are forecasts submitted between the 8th of March 2021 and the 5th of December 2022 for reported cases and deaths from COVID-19. Target dates range from the 13th of March 2021 to the 10th of December 2022, for a total of 92 weeks. See \cite{sherrattPredictivePerformanceMultimodel2022} for a more thorough description of the data. We filtered all forecasts submitted to the Hub to only include the seven models which have submitted forecasts for both deaths and cases for 4 horizons in 32 locations on at least 46 forecast dates (see Figure \ref{fig:HUB-num-avail-models}). We removed all observations marked as data anomalies by the European Forecast Hub \citep{sherrattPredictivePerformanceMultimodel2022} as well as all remaining negative observed values. These anomalies made up a relevant fraction of all observations. On average across locations, 12.1 out of 92 (13.2\%) observations were removed for cases and 12.4 out of 92 (13.5\%) for deaths. Figure \ref{fig:number-anomalies} displays the number of anomalies removed for each location. In addition, we filtered out erroneous forecasts that were in extremely poor agreement with the observed data, as defined by any of the conditions listed in Table \ref{tab:erroneous}. Figure \ref{fig:erroneous-forecasts.png} shows the percentage of forecasts removed for each model. Those few (less than 0.2\%  of forecasts for each model) erroneous outlier forecasts had excessive influence on average scores and relative skill scores in a way that was not representative of normal model behaviour. We removed them here in order to better illustrate the effects of the log-transformation on scores that one would expect in a 'normal' scenario. In a regular forecast evaluation such erroneous forecasts should usually not be removed and would count towards overall model scores.

@@

\subsection{Impact of logarithmic transformation on model rankings}

@@

It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations (potentially after standardising different scores to have the same mean and standard deviation). This would make it possible to create custom scores and allow forecast consumers to choose and assign explicit weights to different qualities of the forecasts they might care about.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-model-comparison-baseline.png}
    \caption{
    Forecasts and scores for two-week-ahead predictions from the EuroCOVIDhub-baseline made in Germany. The model had zero included in some of its 50 percent intervals (e.g. for case forecasts in July 2021), leading to excessive dispersion values on the log scale. One could argue that including zero in the prediction intervals constituted an unreasonable forecast that was rightly penalised, but in general care has to be taken with small numbers. A, E: 50\% and 90\% prediction intervals and observed values for cases and deaths on the natural scale. B, F: Corresponding scores. C, G: Forecasts and observations on the log scale. D, H: Corresponding scores. 
    }
    \label{fig:HUB-model-comparison-baseline}
\end{figure}

>>>>

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. 
Proper scoring rules are constructed such that they encourage honest forecasting and cannot be `gamed' or `cheated'. 
Assuming that the forecaster's actual best judgement corresponds to a predictive distribution $F$, a proper score is constructed such that under $F$, no other distribution $G$ yields a better expected score. Forecasters (anyone or anything that issues a forecast) are thus incentivised to report their true belief $F$ about the future. Common proper scoring rules are the logarithmic or log score \citep{goodRationalDecisions1952} or the continuous ranked probability score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007}. The log score is the log-likelihood of the predictive density at the observed value and is scale-invariant under monotonous transformations. The log score does not suffer from the issues we address in this paper, but due to a number of reasons is not as widely used in fields such as weather forecasting or epidemiology (see e.g., \citealt{Johansson2019} for an exception). For example, the log score assigns particularly severe penalties to occasional misguided forecasts. This lack of robustness may limit its practical applicability \cite{bracherEvaluatingEpidemicForecasts2021}. Moreover, it is not easily applied to forecasts reported as samples or quantiles, as used in many recent disease forecasting efforts. 
For these reasons, the CRPS or its discrete equivalent, the ranked probability score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the weighted interval score ~\citep[WIS,][]{bracherEvaluatingEpidemicForecasts2021} are more commonly used in epidemiology.

@@

For conceptual clarity and to allow for a more in-depth discussion, we focus mostly on the natural logarithm as a particular transformation in the context of epidemic phenomena. We refer to this transformation as 'log-transformation' and to scores that have been computed from log-transformed forecasts and observations as scores 'on the log scale' (as opposed to scores 'on the natural scale', which involve no transformation). In the theoretical discussion in Section \ref{sec:methods}, 'log-transformation' and 'log scale' generally refer to a transformation of $\log_{e}(x)$. For practical applications (Section \ref{sec:HUB}) we also use these terms to describe a transformation of $\log_{e}(x + \varepsilon)$ in order to keep the terminology and notation simple. For a prediction target with strictly positive support, the CRPS after applying a log-transformation is given by
%
\begin{linenomath*}
\begin{equation}
    \text{CRPS}(F_{\log}, \log y) = \int_{-\infty}^\infty \left( F_{\log}(x) - \boldsymbol{1}(x \geq \log y) \right)^2 dx.
\end{equation}    
\end{linenomath*}
%
Here, $y$ is again the observed outcome and $F_{\log}$ is the predictive CDF of the log-transformed outcome, i.e.,
\begin{linenomath*}
\begin{equation}
F_{\log}(x) = F(\exp(x)),
\end{equation}    
\end{linenomath*}
with $F$ the CDF on the original scale. Instead of a score representing the magnitude of absolute errors, applying a log-transformation prior to the CRPS yields a score which a) measures relative error (see Section \ref{sec:methods:relative}), b) provides a measure for how well a forecast captures the exponential growth rate of the target quantity (see Section \ref{sec:methods:growthrate}) and c) is less dependent on the expected order of magnitude of the quantity to be predicted (see Section \ref{sec:methods:vst}). 
We therefore argue that such evaluations on the logarithmic scale should complement the prevailing evaluations on the natural scale. 
Other transformations may likewise be of interest. We briefly explore the square root transformation as an alternative transformation. 
Our analysis mostly focuses on the CRPS (or WIS) as an evaluation metric for probabilistic forecasts, given its widespread use throughout the COVID-19 pandemic.

@@

To illustrate the effect of applying the natural logarithm prior to evaluating forecasts we consider the absolute error, which the CRPS and WIS generalize to probabilistic forecasts. We assume strictly positive support (meaning that no specific handling of zero values is needed), a restriction we will address when applying this transformation in practice. When considering a point forecast $\hat{y}$ for a quantity of interest $y$, such that 
%
\begin{linenomath*}
\begin{equation}
y = \hat{y} + \varepsilon,
\end{equation}
\end{linenomath*}
the absolute error is given by $|\varepsilon|$. When taking the logarithm of the forecast and the observation first, thus considering 
\begin{linenomath*}
\begin{equation}
\log y = \log \hat{y} + \varepsilon^*,
\end{equation}
\end{linenomath*}
the resulting absolute error $\left|\varepsilon^*\right|$ can be interpreted as an approximation of various common relative error measures. Using that $\log(a) \approx a - 1$ if $a$ is close to 1, we get
\begin{linenomath*}
\begin{equation}
|\varepsilon^*| = |\log \hat{y} - \log y| = \left|\log\left(\frac{\hat{y}}{y}\right) \right| \ \ \stackrel{\text{if } \hat{y} \ \approx \ y}{\approx} \ \ \left| \frac{\hat{y}}{y} - 1 \right| \ \ = \ \ \left| \frac{\hat{y} - y}{y} \right|.
\end{equation}
\end{linenomath*}
The absolute error after log transforming is thus an approximation of the \textit{absolute percentage error} \citep[APE,][]{gneitingMakingEvaluatingPoint2011a} as long as forecast and observation are close. As we assumed that $\hat{y} \approx y$, we can also interpret it as an approximation of the \textit{relative error} \citep[RE,][]{gneitingMakingEvaluatingPoint2011a}
\begin{linenomath*}
\begin{equation}
\left| \frac{\hat{y} - y}{\hat{y}} \right|
\end{equation}
\end{linenomath*}
and the \textit{symmetric absolute percentage error} (SAPE; see e.g., \citealt{Flores1986})
\begin{linenomath*}
\begin{equation}
\left| \ \frac{\hat{y} - y}{y/2 + \hat{y}/2} \ \right|.
\end{equation}
\end{linenomath*}
As Figure \ref{fig:SAPE} shows, the alignment with the SAPE is in fact the closest and holds quite well even if predicted and observed value differ by a factor of two or three. Generalising to probabilistic forecasts, the CRPS applied to log-transformed forecasts and outcomes can thus be seen as a probabilistic counterpart to the symmetric absolute percentage error, which offers an appealing intuitive interpretation.

@@

When evaluating models across sets of forecasting tasks, it may be desirable for each target to have a similar impact on the overall results. This could be motivated by the assumption that forecasts from different geographical units and time periods provide similar amounts of information about how well a forecaster performs. One would then like the resulting scores to be independent of the order of magnitude of the target to predict. CRPS values on the natural scale, however, typically scale with the order of magnitude of the quantity to be predicted. Average scores are then dominated by the results achieved for targets with high expected outcomes in a way that does not necessarily reflect the underlying predictive ability well.

@@

If the mean-variance relationship of the data-generating distribution is quadratic with $\sigma^2 = c \times \mu^2$, the natural logarithm can serve as the VST \citep{guerreroTimeseriesAnalysisSupported1993}. Denoting by $F_{\log}$ the predictive distribution for $\log(Y)$, we can use the delta method (a first-order Taylor approximation, see e.g., \citealt{Dunn2018}), to show that

\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.\label{eq:taylor_quadratic}
\end{equation}
\end{linenomath*}
As $\sigma$ and $\mu$ are linked through the quadratic mean-variance relationship ($\sigma = \sqrt{c} \times \mu$), the expected CRPS stays constant regardless of the expeccted value of the data-generating distribution $\mu$. The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections \ref{sec:methods:relative} and \ref{sec:methods:growthrate}. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome, i.e. does not depend on the current phase of the epidemic or the order of magnitude of current observations.

@@

Transformations that are strictly monotonic are permissible in the sense that resulting scores remain proper. This is because even though rankings of models may change forecasts will in expectation still minimise their score if they report a predictive distribution that is equal to the data-generating distribution. This condition holds for both the log and square root transformations, as well as many others. However, the order of the operations matters, and applying a transformation after scores have been computed generally does not guarantee that the score remains proper. In the case of log transforms, taking the logarithm of the scores, rather than scoring the log-transformed forecasts and data, results in an improper score. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can be seen that in the example overconfident models perform best in terms of the log WIS.

In practice, one issue with the log transform is that they are not readily applicable to negative numbers or zero values, which need to be removed or otherwise handled. 
One common approach to deal with zeros is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm \citep{bellegoDealingLogsZeros2022}. This represents a strictly monotonic transformation and therefore guarantees that the resulting score remains proper. The choice of the quantity to add does however influence scores and rankings, as measures of relative errors shrink when adding a constant $a$ to the forecast and the observation. We illustrate this in Figure \ref{fig:illustration-effect-log-offset}. As a rule of thumb, if if $x > 5a$, the difference between $\log{(x + a)}$ and $\log{(x)}$ is small, and it becomes negligible if $x > 50a$. Choosing a suitable offset $a$ balances two competing concerns: on the one hand, choosing a small $a$ makes sure that the transformation is as close to a natural logarithm as possible and scores can be interpreted as outlined above. On the other hand, choosing a larger $a$ can help stabilise scores for forecasts and observations close to zero, avoiding giving excessive weight to forecasts for small quantities (see Figure \ref{fig:HUB-log-different-offsets}). For large values of $a$, $\log(x + a)$ grows linearly in $x$, meaning that we expect to observe the same patterns as in the case with no transformation. For decreasing values of $a$, we give more relative weight to scores in small locations.

A related issue occurs when the predictive distribution has a large probability mass on zero (or on very small values), as this can translate into an excessively wide forecast in relative terms. This can be seen in Figure \ref{fig:HUB-model-comparison-baseline}. Here, the dispersion component of the WIS is inflated for scores obtained after applying the natural logarithm because forecasts contained zero in its prediction intervals. To deal with this issue one could potentially choose to use a higher $a$ value when applying a transformation $\log(x + a)$, for example $a = 10$ instead of the $a = 1$ that we chose to use.

@@

\subsection{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on the CRPS may change when making use of a transformation, both in terms of aggregate and individual scores. We illustrate this in Figure \ref{fig:illustration-ranking} with two forecasters, A and B, issuing two different distributions with different dispersion. When showing the obtained CRPS as a function of the observed value, it can be seen that the ranking between the two forecasters may change when scoring the forecast on the logarithmic, rather than the natural scale. In particular, on the natural scale, forecaster A, who issues a more uncertain distribution, receives a better score than forecaster B for observed values far away from the centre of the respective predictive distribution. On the log scale, however, forecaster A receives a lower score for large observed values, being more heavily penalised for assigning large probability to small values (which, in relative terms, are far away from the actual observation). We note that the chosen example involving a geometric forecast distribution is somewhat constructed; as shown in Section \ref{sec:Hub:cor} and Figure \ref{fig:HUB-cors}A, rankings between models usually stay quite stable for a single forecast.

.

@@

The forecasts used for the purpose of this illustration are forecasts submitted between the 8th of March 2021 and the 5th of December 2022 for reported cases and deaths from COVID-19. Target dates range from the 13th of March 2021 to the 10th of December 2022, for a total of 92 weeks. See \cite{sherrattPredictivePerformanceMultimodel2022} for a more thorough description of the data. We filtered all forecasts submitted to the Hub to only include the seven models which have submitted forecasts for both deaths and cases for 4 horizons in 32 locations on at least 46 forecast dates (see Figure \ref{fig:HUB-num-avail-models}). We removed all observations marked as data anomalies by the European Forecast Hub \citep{sherrattPredictivePerformanceMultimodel2022} as well as all remaining negative observed values. These anomalies made up a relevant fraction of all observations. On average across locations, 12.1 out of 92 (13.2\%) observations were removed for cases and 12.4 out of 92 (13.5\%) for deaths. Figure \ref{fig:number-anomalies} displays the number of anomalies removed for each location. In addition, we filtered out a small number of erroneous forecasts that were in extremely poor agreement with the observed data, as defined by any of the conditions listed in Table \ref{tab:erroneous}. Figure \ref{fig:erroneous-forecasts.png} shows the percentage of forecasts removed for each model. Those few (less than 0.2\%  of forecasts for each model) erroneous outlier forecasts had excessive influence on average scores and relative skill scores in a way that was not representative of normal model behaviour. We removed them here in order to better illustrate the effects of the log-transformation on scores that one would expect in a well-behaved scenario. In a regular forecast evaluation such erroneous forecasts should usually not be removed and would count towards overall model scores.

@@

\subsection{Impact of logarithmic transformation on model rankings}
\label{sec:Hub:cor}

@@

It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations. This would make it possible to create custom scores and allow forecast consumers to choose and assign explicit weights to different qualities of the forecasts they might care about.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-model-comparison-baseline.png}
    \caption{
    Forecasts and scores for two-week-ahead predictions from the EuroCOVIDhub-baseline made in Germany. The model had zero included in some of its 50 percent intervals (e.g. for case forecasts in July 2021), leading to excessive dispersion values on the log scale. One could argue that including zero in the prediction intervals constituted an unreasonable forecast that was rightly penalised, but in general care has to be taken with small numbers. One potential way to do deal with this could be to use a higher $a$ value when applying a transformation $\log(x + a)$, for example $a = 10$ instead of $a = 1$. A, E: 50\% and 90\% prediction intervals and observed values for cases and deaths on the natural scale. B, F: Corresponding scores. C, G: Forecasts and observations on the log scale. D, H: Corresponding scores. 
    }
    \label{fig:HUB-model-comparison-baseline}
\end{figure}
